My Cool Title

### 2019-04-29 paper.tex
Added todo command. Added contributions list

@@

Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
To enable this, we implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.

>>>>

% Package for todo command
\usepackage{xcolor}

\newcommand\todo[1]{\textcolor{red}{#1}}

@@

Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.

This work includes the following contributions:

\begin{itemize}
  \item a POMDP-based human controller that enables object search and guidance on a mobile phone;
  \item experiments that evaluate the efficacy of the proposed system.
\end{itemize}

\todo{Add paper layout}
